Method

### 2025-11-26 GroupPolarizationStatmod/paper/method.qmd
expanded method with error rates table

@@

>>>>

The core of our evaluation is the quantification of the probability that a spurious result—an effect generated by the null model—is falsely interpreted as genuine group polarization. We calculate this probability across three distinct units of analysis, building from the specific to the general:

1. The Type I Error Rate ($\alpha_e$): The rate of falsely detecting group polarization in a single experimental condition ($e$). This directly quantifies the risk posed by the mere agreement model identified for that specific experiment.
2. The study-level Family-Wise Error Rate ($\alpha_s$): The mean Type I Error Rate aggregated across all conditions within a single study ($s$). This estimates the false claim rate across the set of tests performed in that study.
3. The Family-Wise Error Rate ($\alpha_{\text{all}}$): The mean Type I Error Rate aggregated across all 57 experimental conditions in the corpus ($E$). This estimates the expected false claim rate for a researcher adopting the general experimental design found throughout the literature.

These calculated Type I Error Rates ($\alpha$) are then combined with fixed external parameters to estimate the False Discovery Rate. Following convention, we adopt a fixed Statistical Power of $W=0.80$ (and test sensitivity with alternative values) and a Base Rate of $b=0.10$. The relationship between the units of analysis and the estimated error rates is summarized in Table @tbl-error-rates.

{{< include Error-Rates-Table.html >}}

@@

### Statistical Inference Pipeline

To complete our our simulated experimental design we need to be able to
statistically infer the effect sizes that measure the strength of group
polarization in an experiment. To keep the presentation simple and transparent,
we infer effect sizes by inferring the parameters $\mu_t$ and $\sigma_t$ of the
hypothesized normal distribution that generates the data—*literally* generates
the data in our simulations, but is just a model of the distribution of group
opinions in real-world experiments.
